---
title: "Analysis of Streaming Transactions"
subtitle: "Based on Data Collected by SportsTV Germany"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
  html_document:
    toc: true
    toc_float:
      collapsed: true
    toc_depth: 2
    number_sections: true
    theme: paper
    highlight: tango
author: "Karthik Bharadwaj and Akshay Mambakkam Sridharan"
---
```{r setup, include=FALSE, author="Akshay Mambakkam Sridharan"}
# Clean environment
rm(list = ls())

if (!require("DBI")) install.packages("DBI")
if (!require("RMySQL")) install.packages("RMySQL")
if (!require("knitr")) install.packages("knitr")
if (!require("kableExtra")) install.packages("kableExtra")

library(DBI)
library(RMySQL)
library(knitr)
library(kableExtra)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r connectMySql, include=FALSE, author="Akshay Mambakkam Sridharan"}
connectToMySql <- function() {
  db_host <- Sys.getenv("MYSQL_HOST")
  db_port <- as.integer(Sys.getenv("MYSQL_PORT", unset = "3306"))
  db_name <- Sys.getenv("MYSQL_DB")
  db_user <- Sys.getenv("MYSQL_USER")
  db_pwd  <- Sys.getenv("MYSQL_PWD")

  if (any(c(db_host, db_name, db_user, db_pwd) == "")) {
    stop("Missing MySQL credentials. Set MYSQL_HOST, MYSQL_PORT, MYSQL_DB, MYSQL_USER, MYSQL_PWD (e.g. in .Renviron).")
  }

  mySqlDB <- tryCatch({
    dbConnect(RMySQL::MySQL(),
              user = db_user,
              password = db_pwd,
              dbname = db_name,
              host = db_host,
              port = db_port)
  }, error = function(e) {
    cat("Error connecting to MySQL:", e$message, "\n")
    stop("Could not connect to MySQL database")
  })
  
  return(mySqlDB)
}

disconnectMySql <- function(mySqlDB) {
  dbDisconnect(mySqlDB)
}

mysqlConn <- connectToMySql()
```

# Data Breakdown
```{r executiveSummary, echo=FALSE, author="Akshay Mambakkam Sridharan"}
summaryQuery <- "
SELECT 
  COUNT(*) as total_fact_rows,
  SUM(transaction_count) as total_transactions,
  SUM(total_minutes_streamed) as total_minutes,
  SUM(total_minutes_streamed) / SUM(transaction_count) as avg_session_minutes,
  SUM(completed_count) as completed_streams
FROM fact_streaming_analytics
"
summaryData <- dbGetQuery(mysqlConn, summaryQuery)

# Get date range from dimension table
dateRangeQuery <- "SELECT MIN(date_value) as min_date, MAX(date_value) as max_date FROM dim_date"
dateRange <- dbGetQuery(mysqlConn, dateRangeQuery)

# Get dimension counts
dimCountsQuery <- "
SELECT 
  (SELECT COUNT(*) FROM dim_country) as countries,
  (SELECT COUNT(*) FROM dim_sport) as sports,
  (SELECT COUNT(*) FROM dim_device) as devices,
  (SELECT COUNT(*) FROM dim_quality) as quality_levels
"
dimCounts <- dbGetQuery(mysqlConn, dimCountsQuery)

totalTransactions <- summaryData$total_transactions
totalMinutes <- summaryData$total_minutes
totalHours <- round(totalMinutes / 60, 0)
avgSessionMinutes <- round(summaryData$avg_session_minutes, 1)
completedStreams <- summaryData$completed_streams
completionRate <- round((completedStreams / totalTransactions) * 100, 1)

uniqueUsers <- dbGetQuery(mysqlConn, "SELECT stat_value FROM summary_stats WHERE stat_name = 'unique_users'")$stat_value
```

This report presents a comprehensive analysis of streaming transaction data for SportsTV Germany, a platform specializing in the distribution of amateur sporting event recordings. The dataset spans **`r dateRange$min_date`** through **`r dateRange$max_date`**, representing comprehensive platform activity stored in a **dimensional data warehouse** with partitioned fact tables.

**Key Performance Metrics:**

- **Total Streaming Transactions:** `r format(totalTransactions, big.mark = ",")`
- **Total Hours Streamed:** `r format(totalHours, big.mark = ",")` hours
- **Average Session Duration:** `r avgSessionMinutes` minutes
- **Completion Rate:** `r completionRate`%
- **Geographic Coverage:** `r dimCounts$countries` countries
- **Sport Categories:** `r dimCounts$sports` sports
- **Device Types:** `r dimCounts$devices` devices
- **Quality Levels:** `r dimCounts$quality_levels` quality levels
- **Unique Users:** `r format(uniqueUsers, big.mark = ",")`

---

# Growth of streaming transactions by streaming time and number of streaming events by sport
```{r growthData, echo=FALSE, author="Akshay Mambakkam Sridharan"}
# Query using dimension table joins
growthQuery <- "
SELECT 
  d.year,
  s.sport,
  SUM(f.total_minutes_streamed) as total_minutes,
  SUM(f.transaction_count) as total_transactions
FROM fact_streaming_analytics f
JOIN dim_date d ON f.date_key = d.date_id
JOIN dim_sport s ON f.sport_key = s.sport_key
GROUP BY d.year, s.sport
ORDER BY d.year, s.sport
"
growthData <- dbGetQuery(mysqlConn, growthQuery)

totalYears <- length(unique(growthData$year))
minYear <- min(growthData$year)
maxYear <- max(growthData$year)

iceHockeyData <- growthData[growthData$sport == "Ice Hockey", ]
inlineHockeyData <- growthData[growthData$sport == "Inline Hockey", ]
skiJumpingData <- growthData[growthData$sport == "Ski Jumping", ]
```

This analysis covers a **`r totalYears`-year period** of streaming activity, with data collected from **`r minYear`** through **`r maxYear`**.

## Growth in Streaming Events by Sport
```{r growthEventsChart, echo=FALSE, fig.width=10, fig.height=6, author="Akshay Mambakkam Sridharan"}
yMax <- max(growthData$total_transactions / 1000) * 1.1

plot(iceHockeyData$year, iceHockeyData$total_transactions / 1000,
     type = "b", col = "darkblue", lwd = 2, pch = 16, cex = 1.5,
     xlab = "Year", ylab = "Number of Streaming Events (Thousands)",
     main = "Growth in Streaming Events by Sport",
     ylim = c(0, yMax))

lines(inlineHockeyData$year, inlineHockeyData$total_transactions / 1000,
      type = "b", col = "red", lwd = 2, pch = 17, cex = 1.5)

lines(skiJumpingData$year, skiJumpingData$total_transactions / 1000,
      type = "b", col = "steelblue", lwd = 2, pch = 18, cex = 1.5)

legend("topleft", legend = c("Ice Hockey", "Inline Hockey", "Ski Jumping"),
       col = c("darkblue", "red", "steelblue"), lwd = 2, pch = c(16, 17, 18), bty = "n")

grid(col = "lightgray")
```

## Growth in Streaming Time by Sport
```{r growthTimeChart, echo=FALSE, fig.width=10, fig.height=6, author="Karthik Bharadwaj"}
yMaxTime <- max(growthData$total_minutes / 60000) * 1.1

plot(iceHockeyData$year, iceHockeyData$total_minutes / 60000,
     type = "b", col = "darkblue", lwd = 2, pch = 16, cex = 1.5,
     xlab = "Year", ylab = "Total Hours Streamed (Thousands)",
     main = "Growth in Streaming Time by Sport",
     ylim = c(0, yMaxTime))

lines(inlineHockeyData$year, inlineHockeyData$total_minutes / 60000,
      type = "b", col = "red", lwd = 2, pch = 17, cex = 1.5)

lines(skiJumpingData$year, skiJumpingData$total_minutes / 60000,
      type = "b", col = "steelblue", lwd = 2, pch = 18, cex = 1.5)

legend("topleft", legend = c("Ice Hockey", "Inline Hockey", "Ski Jumping"),
       col = c("darkblue", "red", "steelblue"), lwd = 2, pch = c(16, 17, 18), bty = "n")

grid(col = "lightgray")
```

## Year-over-Year Growth Summary
```{r growthTable, echo=FALSE, author="Akshay Mambakkam Sridharan"}
growthWide <- reshape(growthData[, c("year", "sport", "total_transactions")],
                      idvar = "year",
                      timevar = "sport",
                      direction = "wide")

colnames(growthWide) <- c("Year", "Ice Hockey", "Inline Hockey", "Ski Jumping")

growthWide$Total <- rowSums(growthWide[, 2:4])

kable(growthWide,
      format = "html",
      format.args = list(big.mark = ","),
      caption = "Streaming Transactions by Sport and Year") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, background = "steelblue", color = "white")
```
```{r growthAnalysis, echo=FALSE, author="Karthik Bharadwaj"}
totalBySport <- aggregate(total_transactions ~ sport, growthData, sum)
topSport <- totalBySport[which.max(totalBySport$total_transactions), "sport"]
topSportTotal <- totalBySport[which.max(totalBySport$total_transactions), "total_transactions"]

totalByYear <- aggregate(total_transactions ~ year, growthData, sum)
peakYear <- totalByYear[which.max(totalByYear$total_transactions), "year"]
peakYearTotal <- totalByYear[which.max(totalByYear$total_transactions), "total_transactions"]
```

**Key Findings:** The data reveals that **`r topSport`** is the most popular sport on the platform, accounting for **`r format(topSportTotal, big.mark = ",")`** transactions. Streaming activity peaked in **`r peakYear`** with **`r format(peakYearTotal, big.mark = ",")`** transactions recorded.

---

# Number of streaming events per week for the most recent year
```{r weeklyData, echo=FALSE, author="Karthik Bharadwaj"}
recentYear <- maxYear

weeklyQuery <- sprintf("
SELECT 
  d.week,
  SUM(f.transaction_count) as total_transactions,
  SUM(f.total_minutes_streamed) as total_minutes
FROM fact_streaming_analytics f
JOIN dim_date d ON f.date_key = d.date_id
WHERE d.year = %d
GROUP BY d.week
ORDER BY d.week
", recentYear)

weeklyData <- dbGetQuery(mysqlConn, weeklyQuery)

totalWeeks <- nrow(weeklyData)
avgWeeklyTransactions <- round(mean(weeklyData$total_transactions), 0)
peakWeek <- weeklyData$week[which.max(weeklyData$total_transactions)]
peakWeekTransactions <- max(weeklyData$total_transactions)
lowWeek <- weeklyData$week[which.min(weeklyData$total_transactions)]
lowWeekTransactions <- min(weeklyData$total_transactions)
```

## Weekly Transaction Volume
```{r weeklyChart, echo=FALSE, fig.width=12, fig.height=6, author="Karthik Bharadwaj"}
barColors <- rep("steelblue", length(weeklyData$week))
barColors[which.max(weeklyData$total_transactions)] <- "darkblue"
barColors[which.min(weeklyData$total_transactions)] <- "red"

barplot(weeklyData$total_transactions,
        names.arg = weeklyData$week,
        col = barColors,
        xlab = "Week Number",
        ylab = "Number of Transactions",
        main = paste("Weekly Streaming Events in", recentYear),
        las = 1,
        border = NA)

abline(h = avgWeeklyTransactions, col = "red", lty = 2, lwd = 2)

legend("topright", 
       legend = c("Peak Week", "Lowest Week", "Average"),
       fill = c("darkblue", "red", NA),
       border = c("darkblue", "red", NA),
       lty = c(NA, NA, 2),
       lwd = c(NA, NA, 2),
       col = c(NA, NA, "red"),
       bty = "n")

grid(nx = NA, ny = NULL, col = "lightgray")
```

In **`r recentYear`**, the platform recorded **`r format(sum(weeklyData$total_transactions), big.mark = ",")`** streaming events totaling **`r format(round(sum(weeklyData$total_minutes) / 60), big.mark = ",")`** hours across **`r totalWeeks` weeks**. Weekly transactions averaged **`r format(avgWeeklyTransactions, big.mark = ",")`**, peaking at **`r format(peakWeekTransactions, big.mark = ",")`** in week **`r peakWeek`** and dropping to **`r format(lowWeekTransactions, big.mark = ",")`** in week **`r lowWeek`**.

## Weekly Statistics Summary
```{r weeklyStats, echo=FALSE, author="Karthik Bharadwaj"}
weeklyStats <- data.frame(
  Metric = c("Average Weekly Transactions", "Peak Week", "Peak Week Transactions", 
             "Lowest Week", "Lowest Week Transactions", "Week-to-Week Variance"),
  Value = c(format(avgWeeklyTransactions, big.mark = ","),
            peakWeek,
            format(peakWeekTransactions, big.mark = ","),
            lowWeek,
            format(lowWeekTransactions, big.mark = ","),
            paste0(round(sd(weeklyData$total_transactions) / avgWeeklyTransactions * 100, 1), "%"))
)

kable(weeklyStats,
      format = "html",
      col.names = c("Metric", "Value"),
      caption = paste("Weekly Streaming Statistics for", recentYear)) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, background = "steelblue", color = "white")
```

---

# Average streaming time and total number of streams by sport and by country
```{r sportCountryData, echo=FALSE, author="Karthik Bharadwaj"}
sportCountryQuery <- "
SELECT 
  s.sport,
  c.country,
  SUM(f.transaction_count) as total_streams,
  SUM(f.total_minutes_streamed) as total_minutes,
  SUM(f.total_minutes_streamed) / SUM(f.transaction_count) as avg_minutes
FROM fact_streaming_analytics f
JOIN dim_sport s ON f.sport_key = s.sport_key
JOIN dim_country c ON f.country_key = c.country_key
GROUP BY s.sport, c.country
ORDER BY s.sport, total_streams DESC
"
sportCountryData <- dbGetQuery(mysqlConn, sportCountryQuery)
```

## Average Streaming Duration by Sport and Country
```{r avgDurationChart, echo=FALSE, fig.width=10, fig.height=6, author="Akshay Mambakkam Sridharan"}
countries <- unique(sportCountryData$country)
sports <- unique(sportCountryData$sport)

avgMatrix <- matrix(0, nrow = length(sports), ncol = length(countries))
rownames(avgMatrix) <- sports
colnames(avgMatrix) <- countries

for (i in 1:nrow(sportCountryData)) {
  sport <- sportCountryData$sport[i]
  country <- sportCountryData$country[i]
  avgMatrix[sport, country] <- sportCountryData$avg_minutes[i]
}

barplot(avgMatrix,
        beside = TRUE,
        col = c("darkblue", "red", "steelblue"),
        xlab = "Country",
        ylab = "Average Minutes per Session",
        main = "Average Streaming Duration by Sport and Country",
        las = 1)

legend("topright", legend = sports,
       fill = c("darkblue", "red", "steelblue"), bty = "n")

grid(nx = NA, ny = NULL, col = "lightgray")
```

## Total Streams by Sport and Country
```{r totalStreamsChart, echo=FALSE, fig.width=10, fig.height=6, author="Akshay Mambakkam Sridharan"}
totalMatrix <- matrix(0, nrow = length(sports), ncol = length(countries))
rownames(totalMatrix) <- sports
colnames(totalMatrix) <- countries

for (i in 1:nrow(sportCountryData)) {
  sport <- sportCountryData$sport[i]
  country <- sportCountryData$country[i]
  totalMatrix[sport, country] <- sportCountryData$total_streams[i]
}

barplot(totalMatrix / 1000,
        beside = TRUE,
        col = c("darkblue", "red", "steelblue"),
        xlab = "Country",
        ylab = "Total Streams (Thousands)",
        main = "Total Streaming Volume by Sport and Country",
        las = 1)

legend("topright", legend = sports,
       fill = c("darkblue", "red", "steelblue"), bty = "n")

grid(nx = NA, ny = NULL, col = "lightgray")
```

## Detailed Statistics Table
```{r sportCountryTable, echo=FALSE, author="Akshay Mambakkam Sridharan"}
displayData <- sportCountryData[, c("sport", "country", "total_streams", "avg_minutes", "total_minutes")]
displayData$total_hours <- round(displayData$total_minutes / 60, 0)
displayData$avg_minutes <- round(displayData$avg_minutes, 1)

kable(displayData[, c("sport", "country", "total_streams", "avg_minutes", "total_hours")],
      format = "html",
      format.args = list(big.mark = ","),
      col.names = c("Sport", "Country", "Total Streams", "Avg Duration (min)", "Total Hours"),
      caption = "Streaming Statistics by Sport and Country") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, background = "steelblue", color = "white")
```

---

# Day of the week during which the most amount of content is streamed

This section analyzes which days of the week generate the most streaming activity, aggregated over the past three years by sport and country.
```{r dowData, echo=FALSE, author="Akshay Mambakkam Sridharan"}
threeYearsAgo <- maxYear - 2

dowQuery <- sprintf("
SELECT 
  d.day_of_week,
  d.day_name,
  s.sport,
  c.country,
  SUM(f.total_minutes_streamed) as total_minutes,
  SUM(f.transaction_count) as total_transactions
FROM fact_streaming_analytics f
JOIN dim_date d ON f.date_key = d.date_id
JOIN dim_sport s ON f.sport_key = s.sport_key
JOIN dim_country c ON f.country_key = c.country_key
WHERE d.year >= %d
GROUP BY d.day_of_week, d.day_name, s.sport, c.country
ORDER BY d.day_of_week, s.sport, c.country
", threeYearsAgo)

dowData <- dbGetQuery(mysqlConn, dowQuery)

dayOrder <- c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat")
```

Analysis period: **`r threeYearsAgo`** to **`r maxYear`** (3 years)

## Overall Day of Week Patterns
```{r overallDowChart, echo=FALSE, fig.width=10, fig.height=6, author="Akshay Mambakkam Sridharan"}
overallDow <- aggregate(total_minutes ~ day_of_week + day_name, dowData, sum)
overallDow <- overallDow[order(overallDow$day_of_week), ]

barColors <- rep("steelblue", 7)
barColors[which.max(overallDow$total_minutes)] <- "darkblue"

barplot(overallDow$total_minutes / 60000,
        names.arg = dayOrder,
        col = barColors,
        xlab = "Day of Week",
        ylab = "Total Hours Streamed (Thousands)",
        main = "Streaming Time by Day of Week (Past 3 Years)",
        las = 1,
        border = NA)

abline(h = mean(overallDow$total_minutes) / 60000, col = "red", lty = 2, lwd = 2)

legend("topright", legend = c("Peak Day", "Average"),
       fill = c("darkblue", NA), border = c("darkblue", NA),
       lty = c(NA, 2), lwd = c(NA, 2), col = c(NA, "red"), bty = "n")

grid(nx = NA, ny = NULL, col = "lightgray")
```
```{r peakDayCalc, echo=FALSE, author="Karthik Bharadwaj"}
peakDayIdx <- which.max(overallDow$total_minutes)
peakDayName <- dayOrder[peakDayIdx]
peakDayMinutes <- overallDow$total_minutes[peakDayIdx]
peakDayHours <- round(peakDayMinutes / 60, 0)
```

**Peak Streaming Day:** `r peakDayName` with `r format(peakDayHours, big.mark = ",")` total hours streamed over the past three years.

## Day of Week by Sport
```{r dowBySportChart, echo=FALSE, fig.width=10, fig.height=6, author="Karthik Bharadwaj"}
dowBySport <- aggregate(total_minutes ~ day_of_week + day_name + sport, dowData, sum)

iceHockeyDow <- dowBySport[dowBySport$sport == "Ice Hockey", ]
iceHockeyDow <- iceHockeyDow[order(iceHockeyDow$day_of_week), ]

inlineHockeyDow <- dowBySport[dowBySport$sport == "Inline Hockey", ]
inlineHockeyDow <- inlineHockeyDow[order(inlineHockeyDow$day_of_week), ]

skiJumpingDow <- dowBySport[dowBySport$sport == "Ski Jumping", ]
skiJumpingDow <- skiJumpingDow[order(skiJumpingDow$day_of_week), ]

dowSportMatrix <- rbind(iceHockeyDow$total_minutes / 60000,
                        inlineHockeyDow$total_minutes / 60000,
                        skiJumpingDow$total_minutes / 60000)

barplot(dowSportMatrix,
        beside = TRUE,
        names.arg = dayOrder,
        col = c("darkblue", "red", "steelblue"),
        xlab = "Day of Week",
        ylab = "Total Hours Streamed (Thousands)",
        main = "Streaming Time by Day of Week and Sport (Past 3 Years)",
        las = 1)

legend("topright", legend = c("Ice Hockey", "Inline Hockey", "Ski Jumping"),
       fill = c("darkblue", "red", "steelblue"), bty = "n")

grid(nx = NA, ny = NULL, col = "lightgray")
```

## Day of Week by Country
```{r dowByCountryChart, echo=FALSE, fig.width=12, fig.height=8, author="Karthik Bharadwaj"}
countries <- unique(dowData$country)
par(mfrow = c(2, 2))

for (ctry in countries) {
  ctryData <- dowData[dowData$country == ctry, ]
  ctryAgg <- aggregate(total_minutes ~ day_of_week + day_name, ctryData, sum)
  ctryAgg <- ctryAgg[order(ctryAgg$day_of_week), ]
  
  barColors <- rep("steelblue", 7)
  barColors[which.max(ctryAgg$total_minutes)] <- "darkblue"
  
  barplot(ctryAgg$total_minutes / 60000,
          names.arg = dayOrder,
          col = barColors,
          main = ctry,
          xlab = "Day of Week",
          ylab = "Hours (Thousands)",
          las = 1,
          border = NA)
  
  grid(nx = NA, ny = NULL, col = "lightgray")
}

par(mfrow = c(1, 1))
```

## Peak Day Summary by Sport and Country
```{r peakDaySummary, echo=FALSE, author="Karthik Bharadwaj"}
peakDays <- do.call(rbind, lapply(split(dowData, list(dowData$sport, dowData$country)), function(df) {
  if (nrow(df) == 0) return(NULL)
  maxIdx <- which.max(df$total_minutes)
  data.frame(
    Sport = df$sport[1],
    Country = df$country[1],
    Peak_Day = df$day_name[maxIdx],
    Total_Hours = round(df$total_minutes[maxIdx] / 60, 0)
  )
}))

rownames(peakDays) <- NULL
peakDays <- peakDays[order(peakDays$Sport, -peakDays$Total_Hours), ]

kable(peakDays,
      format = "html",
      format.args = list(big.mark = ","),
      col.names = c("Sport", "Country", "Peak Day", "Total Hours"),
      caption = "Peak Streaming Day by Sport and Country (Past 3 Years)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, background = "steelblue", color = "white")
```

---

# Device and Quality Analysis
```{r deviceData, echo=FALSE, author="Karthik Bharadwaj"}
deviceQuery <- "
SELECT 
  dv.device_type,
  SUM(f.transaction_count) as total_streams,
  SUM(f.total_minutes_streamed) as total_minutes,
  SUM(f.total_minutes_streamed) / SUM(f.transaction_count) as avg_minutes
FROM fact_streaming_analytics f
JOIN dim_device dv ON f.device_key = dv.device_key
GROUP BY dv.device_type
ORDER BY total_streams DESC
"
deviceData <- dbGetQuery(mysqlConn, deviceQuery)

qualityQuery <- "
SELECT 
  q.quality_streamed,
  SUM(f.transaction_count) as total_streams,
  SUM(f.total_minutes_streamed) as total_minutes
FROM fact_streaming_analytics f
JOIN dim_quality q ON f.quality_key = q.quality_key
GROUP BY q.quality_streamed
ORDER BY total_streams DESC
"
qualityData <- dbGetQuery(mysqlConn, qualityQuery)
```

## Streaming by Device Type
```{r deviceChart, echo=FALSE, fig.width=10, fig.height=6, author="Karthik Bharadwaj"}
deviceColors <- c("darkblue", "steelblue", "lightblue", "red", "darkred", "firebrick")
deviceColors <- deviceColors[1:nrow(deviceData)]

barplot(deviceData$total_streams / 1000,
        names.arg = deviceData$device_type,
        col = deviceColors,
        xlab = "Device Type",
        ylab = "Total Streams (Thousands)",
        main = "Streaming Volume by Device Type",
        las = 2,
        border = NA)

grid(nx = NA, ny = NULL, col = "lightgray")
```
```{r deviceTable, echo=FALSE, author="Karthik Bharadwaj"}
deviceDisplay <- deviceData
deviceDisplay$avg_minutes <- round(deviceDisplay$avg_minutes, 1)
deviceDisplay$total_hours <- round(deviceDisplay$total_minutes / 60, 0)
deviceDisplay$pct_share <- round(deviceDisplay$total_streams / sum(deviceDisplay$total_streams) * 100, 1)

kable(deviceDisplay[, c("device_type", "total_streams", "avg_minutes", "total_hours", "pct_share")],
      format = "html",
      format.args = list(big.mark = ","),
      col.names = c("Device Type", "Total Streams", "Avg Duration (min)", "Total Hours", "% Share"),
      caption = "Streaming Statistics by Device Type") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, background = "steelblue", color = "white")
```

## Streaming by Quality
```{r qualityChart, echo=FALSE, fig.width=10, fig.height=6, author="Karthik Bharadwaj"}
qualityColors <- c("darkblue", "steelblue", "lightblue", "red", "darkred")
qualityColors <- qualityColors[1:nrow(qualityData)]

pie(qualityData$total_streams,
    labels = paste0(qualityData$quality_streamed, "\n", 
                   round(qualityData$total_streams / sum(qualityData$total_streams) * 100, 1), "%"),
    col = qualityColors,
    main = "Distribution of Streaming Quality",
    border = "white")
```
```{r qualityTable, echo=FALSE, author="Karthik Bharadwaj"}
qualityDisplay <- qualityData
qualityDisplay$total_hours <- round(qualityDisplay$total_minutes / 60, 0)
qualityDisplay$pct_share <- round(qualityDisplay$total_streams / sum(qualityDisplay$total_streams) * 100, 1)

kable(qualityDisplay[, c("quality_streamed", "total_streams", "total_hours", "pct_share")],
      format = "html",
      format.args = list(big.mark = ","),
      col.names = c("Quality Level", "Total Streams", "Total Hours", "% Share"),
      caption = "Streaming Statistics by Quality Level") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = FALSE) %>%
  row_spec(0, bold = TRUE, background = "steelblue", color = "white")
```

---
```{r cleanup, include=FALSE, author="Akshay Mambakkam Sridharan"}
disconnectMySql(mysqlConn)
```